Article data analysis

### 2018-10-18 notebooks/article_notebook.Rmd
updated last figure to include n

```{r ARIBA analysis, include = FALSE}
megares_report_loc <- "../data/ariba/megares_results"
resfinder_report_loc <- "../data/ariba/resfinder_results"
ac_genes <- c("qnr","oqx")
mut_genes <- c("gyr","par","marR","soxR","acrR")

@@

@@

## Total resistance mechanisms per animal species
```{r, warning=F, message=F}
total_df <- acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(isolate_data[c("id", "species")])

@@

total_df2 <- total_df %>%
  select(-c(gyrA, gyrB, parC, parE)) %>%
  left_join(cols_to_add, by = "id") %>%
  select(id, species, everything()) %>%
  mutate_at(vars(qnrA1,qnrB19,qnrB6,qnrB60,qnrS1,qnrS2,qnrS4),
            funs(as.numeric(.))) %>%
  mutate(qnr = ifelse(rowSums(.[,3:9]) == 0, 0, 1)) %>%
  select(-c(qnrA1,qnrB19,qnrB6,qnrB60,qnrS1,qnrS2,qnrS4)) %>%
  left_join(mic_data[c("id","CIP")], by = "id") %>%
  select(-id) %>%
  mutate_at(vars(-species, CIP),
            funs(as.numeric(as.character(.)))) %>%
  group_by(species, CIP) %>%
  summarise_all(funs(sum, n = n())) %>%
  select(-c(qnr_n,gyrA_D87G_n,gyrA_D87H_n,
            gyrA_D87N_n,gyrA_D87Y_n,gyrA_S83A_n,
            gyrA_S83L_n,parC_A56T_n,parC_E84V_n,
            parC_S57T_n,parC_S58I_n,parC_S80I_n,
            parC_S80R_n,parE_A512T_n,parE_D463N_n,
            parE_D475E_n,parE_H516Y_n,parE_L416F_n,
            parE_L488M_n,parE_S458A_n)) %>%
  gather(gene, value, -c(species, CIP, marR_n)) %>%
  rename("n" = marR_n) %>%
  mutate(gene2 = sub("(.*?)_(.*?)_sum", "\\1", gene),
         gene2 = sub("(.*?)_sum", "\\1", gene2),
         gene = sub("(.*?)_(.*?)_sum", "\\2", gene),
         gene = sub("(.*?)_sum", "\\1", gene),
         type = case_when(gene2 == "gyrA" ~ 1,
                          gene2 == "gyrB" ~ 2,
                          gene2 == "parC" ~ 3,
                          gene2 == "parE" ~ 4,
                          gene2 == "marR" ~ 5,
                          gene2 == "qnr" ~ 6),
         perc = value/n*100)

ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
  geom_tile(color = "grey70")+
  annotate("rect", xmin = 0, xmax = 6.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("rect", xmin = 6.5, xmax = 12.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("rect", xmin = 12.5, xmax = 19.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("text", x = 3.25, y = -0.05, label = "gyrA", size = 2.5)+
  annotate("text", x = 9.5, y = -0.05, label = "parC", size = 2.5)+
  annotate("text", x = 16, y = -0.05, label = "parE", size = 2.5)+
  scale_fill_viridis(option = "A",
                     begin = 0.1,
                     guide = guide_colorbar(ticks = F,
                                            barheight = 0.5,
                                            barwidth = 10))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 10),
        legend.title = element_blank(),
        legend.position="bottom",
        legend.justification="center",
        legend.direction="horizontal",
        legend.text = element_text(size = 8),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        strip.text = element_text(size = 10))+
  labs(y = "CIP MIC")+
  facet_wrap(~species)+
  coord_fixed()
```

>>>>

```{r ARIBA analysis, include = FALSE}
megares_report_loc <- "../data/ariba/megares_results"
resfinder_report_loc <- "../data/ariba/resfinder_results"
ac_genes <- c("qnr","oqx","qep")
mut_genes <- c("gyr","par","marR","soxR","acrR","mcb")

@@

## Total combinations
```{r}
test <- acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(mic_data[c("id","CIP","NAL")], by = "id") %>%
  left_join(isolate_data[c("id","species")], by = "id") %>%
  select(-id) %>%
  group_by_at(vars(-c(CIP, NAL))) %>%
  summarise(CIP = ifelse(min(as.numeric(CIP)) == max(as.numeric(CIP)),
                         as.character(median(as.numeric(CIP))),
                         paste(min(as.numeric(CIP)), max(as.numeric(CIP)), sep = " - ")),
            NAL = ifelse(min(as.numeric(NAL)) == max(as.numeric(NAL)),
                         as.character(median(as.numeric(NAL))),
                         paste(min(as.numeric(NAL)), max(as.numeric(NAL)), sep = " - ")),
            n = n()) %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,1),
         lwr = round(get_binCI(n, Total)[1],1),
         upr = round(get_binCI(n, Total)[2],1),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

@@

## Total resistance mechanisms per animal species
```{r, warning=F, message=F, fig.height=8, fig.width=12}
AddCol <- function(df, col_name) {
  # split rows by delimeters
  string_to_proc <- df %>% select(!!col_name) %>%
    unlist() %>% str_split(regex("\\, |\\,")) 
  # find unique entries
  unique_strings <- string_to_proc %>%
    unlist() %>% unique()
  # construct names of the new columns
  cols_names <- paste(col_name, unique_strings, sep = "_")
  # construct 0/1-content columns for each unique entry
  cols_content <- sapply(function(i) {
    as.integer(unlist(lapply(function(Z) any(Z %in% unique_strings[i]), 
                             X = string_to_proc)))
  }, X = seq_along(unique_strings))
  res <- data.frame(cols_content)
  names(res) <- cols_names
  return(res)
}

@@

total_df2 <- total_df %>%
  select(-c(gyrA, gyrB, parC, parE)) %>%
  left_join(cols_to_add, by = "id") %>%
  select(id, species, everything()) %>%
  mutate_at(vars(qnrA1,qnrB19,qnrB6,qnrB60,qnrS1,qnrS2,qnrS4),
            funs(as.numeric(.))) %>%
  mutate(qnr = ifelse(rowSums(.[,4:10]) == 0, 0, 1)) %>%
  select(-c(qnrA1,qnrB19,qnrB6,qnrB60,qnrS1,qnrS2,qnrS4)) %>%
  left_join(mic_data[c("id","CIP")], by = "id") %>%
  select(-id) %>%
  mutate_at(vars(-species, CIP),
            funs(as.numeric(as.character(.)))) %>%
  group_by(species, CIP) %>%
  summarise_all(funs(sum, n = n())) %>%
  select(-c(qepA4_n,qnr_n,gyrA_D87G_n,gyrA_D87H_n,
            gyrA_D87N_n,gyrA_D87Y_n,gyrA_S83A_n,
            gyrA_S83L_n,parC_A56T_n,parC_E84V_n,
            parC_S57T_n,parC_S58I_n,parC_S80I_n,
            parC_S80R_n,parE_A512T_n,parE_D463N_n,
            parE_D475E_n,parE_H516Y_n,parE_L416F_n,
            parE_L488M_n,parE_S458A_n)) %>%
  gather(gene, value, -c(species, CIP, marR_n)) %>%
  rename("n" = marR_n) %>%
  mutate(gene2 = sub("(.*?)_(.*?)_sum", "\\1", gene),
         gene2 = sub("(.*?)_sum", "\\1", gene2),
         gene = sub("(.*?)_(.*?)_sum", "\\2", gene),
         gene = sub("(.*?)_sum", "\\1", gene),
         type = case_when(gene2 == "gyrA" ~ 1,
                          gene2 == "gyrB" ~ 2,
                          gene2 == "parC" ~ 3,
                          gene2 == "parE" ~ 4,
                          gene2 == "marR" ~ 5,
                          gene2 == "qnr" ~ 6,
                          gene2 == "qepA4" ~ 7),
         perc = value/n*100)
# 
# ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
#   geom_tile(color = "grey70")+
#   scale_fill_viridis(option = "A",
#                      begin = 0.1,
#                      guide = guide_colorbar(ticks = F,
#                                             barheight = 0.5,
#                                             barwidth = 10))+
#   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 7),
#         axis.text.y = element_text(size = 8),
#         axis.title.x = element_blank(),
#         axis.title.y = element_text(size = 10),
#         legend.title = element_blank(),
#         legend.position="bottom",
#         legend.justification="center",
#         legend.direction="horizontal",
#         legend.text = element_text(size = 8),
#         strip.background = element_rect(colour = "black", fill = "grey70"),
#         strip.text = element_text(size = 10))+
#   labs(y = "CIP MIC")+
#   facet_wrap(~species)+
#   coord_fixed()

p1 <- ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
  geom_tile(color = "grey70")+
  scale_fill_viridis(option = "A",
                     begin = 0.1)+
  guides(fill = FALSE)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 10),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        strip.text = element_text(size = 10),
        plot.margin = unit(c(0,0,0,0), "cm"))+
  labs(y = "CIP MIC")+
  facet_wrap(~species, ncol = 1)+
  coord_fixed()

nplot_data <- total_df %>%
  left_join(mic_data[c("id","CIP")], by = "id") %>%
  group_by(species, CIP) %>%
  count() %>%
  ungroup() %>%
  mutate(species = paste0(species, " n"))

p2 <- ggplot(nplot_data, aes(factor(CIP), n))+
  geom_col()+
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 10),
        axis.ticks.y = element_blank(),
        strip.text = element_text(size = 10),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        plot.margin = unit(c(0,0,-10,0), "cm"))+
  facet_wrap(~species, ncol = 1)+
  coord_flip()

p1g <- ggplotGrob(p1)
p2g <- ggplotGrob(p2)

g <- cbind(p1g, p2g, size = "first")

grid.arrange(g)
